Supplementary Material for the article \textit{Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures}

### 2017-10-13 bn.tex
Edited experiments too

\subsection{LIKELIHOOD}
\label{ssec:likelihood}

@@

\subsection{BAYESIAN STRUCTURE LEARNING}

@@

\subsection {PROBLEMS, SOLUTIONS AND PROBLEMS}

@@

Recently, Suzuki~\cite{Suzuki2017} discussed the theoretical
properties of the BDeu score and showed that in certain settings BDeu
has tendency to add more and more parent variables for a child node
even though the empirical conditional entropy of the child given the
parents has already reached zero. In more detail, assume that in our
data $D$, the values of $X_i$ are completely determined by variables
in set $Z$, so that the empirical entropy $H(X_i | Z) = 0$. Now, if we can further
find one or more variables, denoted by $Y$, whose values are
determined completely by the variables in $Z$, then BDeu will prefer
the set $Z\cup Y$ over $Z$ alone as the parents of $X_i$. Suzuki
argues that this kind of behaviour violates regularity in model
selection as the more complex model is preferred over a simpler one
even though it does not fit the data any better. The phenomenon seems
to stem from the way the hyperparameters for the Dirichlet
distribution are chosen in BDeu as using Jeffreys' prior,
$\theta_{ijk}\sim Dir(\frac{1}{2},\ldots,\frac{1}{2})$, does not suffer
from this anomaly. However, using Jeffreys' prior causes marginal
likelihood score not to be score equivalent.

>>>>

\subsection{Likelihood}
\label{ssec:likelihood}

@@

\subsection{Bayesian Structure Learning}

@@

\subsection {Problems, Solutions and Problems}

@@

Recently, Suzuki~\cite{Suzuki2017} discussed the theoretical
properties of the BDeu score and showed that in certain settings BDeu
has tendency to add more and more parent variables for a child node
even though the empirical conditional entropy of the child given the
parents has already reached zero. In more detail, assume that in our
data $D$, the values of $X_i$ are completely determined by variables
in set $Z$, so that the empirical entropy $H_N(X_i | Z) = 0$. Now, if we can further
find one or more variables, denoted by $Y$, whose values are
determined completely by the variables in $Z$, then BDeu will prefer
the set $Z\cup Y$ over $Z$ alone as the parents of $X_i$. Suzuki
argues that this kind of behaviour violates \textit{regularity} in model
selection as the more complex model is preferred over a simpler one
even though it does not fit the data any better. The phenomenon seems
to stem from the way the hyperparameters for the Dirichlet
distribution are chosen in BDeu as using Jeffreys' prior,
$\theta_{ijk}\sim Dir(\frac{1}{2},\ldots,\frac{1}{2})$, does not suffer
from this anomaly. However, using Jeffreys' prior causes marginal
likelihood score not to be score equivalent. In Section \ref{sec:regularity}, we will give the formal definition of regularity and state that qNML is regular. In addition, we provide a proof of regularity for fNML criterion, which has not appeared in the literature before. The detailed proofs can be found in Appendix A in the Supplementary Material.

### 2017-10-13 intro.tex

\section{INTRODUCTION}
\label{sec:intro}
Bayesian networks~\cite{Pear88} are popular models for presenting
multivariate statistical dependencies that may have been induced by
underlying causal mechanisms.  Techniques for learning the structure
of Bayesian networks from observational data have therefore been used
for many tasks such as discovering cell signaling pathways from
protein activity data~\cite{bn4sigpath02}, revealing the business
process structures~\cite{bn4bpmining} from transaction logs and
modeling brain-region connectivity using fMRI
data~\cite{bn4brainconnect}.

@@

We next briefly introduce Bayesian networks and review the BDeu and
fNML criteria and then introduce the qNML criterion.  We also
summarize the results for 20 data sets to back up our claim that qNML
yields parsimonious models with good predictive capabilities. The
experiments with artificial data demonstrate the capability to give
high scores for the data generating model with relatively small sample
sizes.

>>>>

\section{INTRODUCTION}
\label{sec:intro}
Bayesian networks~\cite{Pear88} are popular models for presenting
multivariate statistical dependencies that may have been induced by
underlying causal mechanisms.  Techniques for learning the structure
of Bayesian networks from observational data have therefore been used
for many tasks such as discovering cell signaling pathways from
protein activity data~\cite{bn4sigpath02}, revealing the business
process structures from transaction logs ~\cite{bn4bpmining} and
modeling brain-region connectivity using fMRI
data~\cite{bn4brainconnect}.

@@

We next briefly introduce Bayesian networks and review the BDeu and
fNML criteria and then introduce the qNML criterion.  We also
summarize the results for 20 data sets to back up our claim that qNML
yields parsimonious models with good predictive capabilities. The
experiments with artificial data generated from real world Bayesian networks demonstrate the capability of our score to quickly learn a structure close to the generating one.
